Running 100,000 Gen

### 2022-06-24 graphs_newt_snakes/running_100000gen.Rmd
looking at some new data

cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
 file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
  cfile$newt_snake_rep <- paste0(cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))

  cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$newt_snake_rep==pattern),]) +
    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col="CA"))+
    #ggtitle(title, subtitle = subt) +
    ylim(-1.1, 1.1)+
    #xlab(x_label_cor) + ylab(y_label)+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      plot.margin=unit(c(-0.5,1,1,1), "cm"))

  file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$newt_snake_rep==pattern),]
  cfile<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$newt_snake_rep==pattern),]
  toDelete <- seq(0, nrow(cfile), 2)
  cfile_short <-  cfile[-toDelete, ]
  figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
    print(paste0("pattern ", pattern))
  print(paste0("Cor between average snake pheno and local cor ", cor(file$Snake_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average newt pheno and local cor ", cor(file$Newt_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average dif pheno and local cor ", cor(file$dif, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between newt pheno and snake ", cor(file$Newt_mean_Pheno, file$Snake_mean_Pheno)))
  return(figure)
}

@@

trends_by_gen <- function(file, title, subt, x_label, y_label){

  plot <- ggplot(file) +
    facet_wrap(~sim)+
    geom_line(aes(generation, dif, group=rep, col="dif"))+
    ggtitle(title, subtitle = subt) +
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    ylim(-5,10)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
labels = c("Snake", "Newt", "Dif"))+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
  return(plot)
}

@@

@@

```{r, graphing by gen}
trends_by_gen(GA1_long_file, title="Space: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations")

trends_by_gen(GA2_long_file, title="Space: Newt VS Snake Population Size GA2", subt="Gen 25sims", y_label="Mean Phenotype", x_label="Generations")

@@

>>>>

cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$rep)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))

  cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col="CA"))+
    #ggtitle(title, subtitle = subt) +
    ylim(-1.1, 1.1)+
    #xlab(x_label_cor) + ylab(y_label)+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      plot.margin=unit(c(-0.5,1,1,1), "cm"))

  file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
  cfile<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
  toDelete <- seq(0, nrow(cfile), 2)
  cfile_short <-  cfile[-toDelete, ]
  figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
    print(paste0("pattern ", pattern))
  print(paste0("Cor between average snake pheno and local cor ", cor(file$Snake_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average newt pheno and local cor ", cor(file$Newt_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average dif pheno and local cor ", cor(file$dif, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between newt pheno and snake ", cor(file$Newt_mean_Pheno, file$Snake_mean_Pheno)))
  return(figure)
}

@@

trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){

  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
    facet_wrap(~sim)+
    geom_line(aes(generation, dif, group=rep, col="dif"))+
    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    geom_hline(yintercept=0, linetype="dashed", color="gray54", size=0.7)+
    ylim(-7,10)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
labels = c("Snake", "Newt", "Dif"))+
    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())
  return(plot)
}

@@

two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
  print(data_points)
dif <- ggplot(file) +

  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+
  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+
  scale_y_continuous(labels = scales::percent)+
  xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      #strip.background = element_blank(), 
                      strip.text.x = element_blank(), 
                      #panel.grid.major = element_blank(), 
                      #panel.grid.minor = element_blank(),
                      #panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

}
two_hist_all_rep(GA1_long_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=25000, max_gen=30000)

@@

```{r, graphing by gen}
trends_by_gen(GA1_long_file, title="Space: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000)

#trends_by_gen(GA2_long_file, title="Space: Newt VS Snake Population Size GA2", subt="Gen 25sims", y_label="Mean Phenotype", x_label="Generations", 1, 50000)

ggsave(
  "~/Desktop/newt_snake_coevo_16.pdf",
  plot = last_plot(),
  scale = 1,
  width = 7,
  height = 5,
  #units = c("in"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL,
)
```

```{r, the scatter of pheno and pop size}
min_gen=5000
max_gen=15000

rep=2

drop_lows <- GA1_long_file[which(GA1_long_file$generation>=min_gen & GA1_long_file$generation<=max_gen & GA1_long_file$rep==rep),]

drop_lows$popsize_dif<-drop_lows$Snake_pop_size-drop_lows$Newt_pop_size
mean(abs(drop_lows$dif))
value=sd(abs(drop_lows$dif))*3

#drop_lows[which(drop_lows$dif>0),]$Newt_mean_Pheno = NA
#drop_lows[which(drop_lows$dif>0),]$Newt_pop_size = NA
#drop_lows[which(drop_lows$dif<0),]$Snake_mean_Pheno = NA
#drop_lows[which(drop_lows$dif<0),]$Snake_pop_size = NA

h <- hist(drop_lows$dif, breaks=18, plot=FALSE)
cuts <- cut(h$breaks, c(-Inf,(abs(min(drop_lows$dif))-value)+min(drop_lows$dif),
                        max(drop_lows$dif)-(max(drop_lows$dif)-value+.5),max(drop_lows$dif)))

#pdf("~/Desktop/dif_in_phenotype_hist.pdf", width = 7, height = 5)
plot(h, col=c("yellow","grey","yellow")[cuts])
#dev.off()

# ggplot(drop_lows[which(abs(drop_lows$dif)>=value),]) +
#   #xlim(0, 1000)+
#   #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
#   #xlab(x_label) + ylab(y_label)+
#   geom_point(aes(x=as.numeric(Newt_mean_Pheno), y=abs(popsize_dif)), color = "darkred",size=3)+
#   geom_point(aes(x=as.numeric(Snake_mean_Pheno), y=abs(popsize_dif)), color = "steelblue",size=3)+
# #  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
#   geom_smooth(aes(x=Newt_mean_Pheno, y=abs(popsize_dif)), method=lm, se=FALSE, fullrange=TRUE, color = "darkred")+
#   geom_smooth(aes(x=Snake_mean_Pheno, y=abs(popsize_dif)), method=lm, se=FALSE, fullrange=TRUE, color = "steelblue")+
#   theme(plot.title = element_text(size=5)) +
#   #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
#   #labs(colour = color_label) +
#   #facet_wrap(~sim)+
#   theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
# 
# ggsave("~/Desktop/dif_in_phenotype_popsize.pdf", plot = last_plot(), scale = 1,
#   width = 7, height = 5, dpi = 300, limitsize = TRUE, bg = NULL)

ggplot(drop_lows)  +
 ggtitle(paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  geom_point(aes(x=as.numeric(dif), y=popsize_dif), color = "darkgreen",size=3)+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
ggsave("~/Desktop/dif_phenotype_dif_popsize.pdf", plot = last_plot(), scale = 1,
  width = 7, height = 5, dpi = 300, limitsize = TRUE, bg = NULL)

ggplot(drop_lows[which(abs(drop_lows$dif)>=value),])  +
  ylim(600, 1200)+
  #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  #xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(Newt_mean_Pheno), y=abs(Newt_pop_size)), color = "darkred",size=3)+
  geom_point(aes(x=as.numeric(Snake_mean_Pheno), y=abs(Snake_pop_size)), color = "steelblue",size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  #geom_smooth(aes(x=Newt_mean_Pheno, y=Newt_pop_size), method=lm, se=FALSE, fullrange=TRUE, color = "darkred")+
  #geom_smooth(aes(x=Snake_mean_Pheno, y=Snake_pop_size), method=lm, se=FALSE, fullrange=TRUE, color = "steelblue")+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))
#ggsave("~/Desktop/phenotype_popsize.pdf", plot = last_plot(), scale = 1,
 # width = 7, height = 5, dpi = 300, limitsize = TRUE, bg = NULL)

@@

two_hist_all_rep(GA1_long_file, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype/100 (green) & Snake-Newt Popsize (purple)",  min_gen=min_gen, max_gen=max_gen)
